---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PEMprepr is a subpackage within the [PEMr](https://github.com/ninoxconsulting/PEMr) family of packages. This package contains functions to prepare all the base data needed to develop sample plans and generate models for building a predictive ecosystem map. As part of the PEMr package users will be provided with a framework of scripts to act as a workflow.


<!-- badges: start -->
[![R-CMD-check](https://github.com/ninoxconsulting/PEMprepr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ninoxconsulting/PEMprepr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of PEMprepr is to ...

## Installation

You can install the development version of PEMprepr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ninoxconsulting/PEMprepr")

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(PEMprepr)
## basic example code
```
